Enhancing the sales prediction of newly published books by means of computational intelligence methods

### 2016-03-29 paper.tex
comentarios
New structure and results in experiments
Still several contents to add and change

% Antonio - El título habría que cambiarlo a otro más descriptivo, creo yo. A ver si os gusta este

%%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%
\author {
P.A. Castillo$^1$, A.M. Mora$^1$, J.J. Merelo$^1$, H. Faris$^2$, \\ P. Garc\'{\i}a-S\'anchez$^1$, A.J. Fern\'andez-Ares$^1$, M.G. Arenas$^1$, P. de las Cuevas$^1$
}
\institute{
$^1$Department of Computer Architecture and Computer Technology. CITIC, ETSIIT. University of Granada (Spain)\\
$^2$Business Information Technology Department. King Abdullah II School for Information Technology. The University of Jordan. Amman (Jordan)\\
           e-mail: {\tt pacv@ugr.es}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
When a new book is launched the publisher faces the problem of
how many books should be printed for delivery to bookstores. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. In this
paper, we are tackling the problem of predicting total sales in order to 
print the right amount of books, doing so even before the book has
reached the shelves. 
Several years 
% % Antonio - Decir cuántos años son, que no me acuerdo.
% of data on published books in Spain have been processed by means of
% data visualisation %visualization does not "process". I propose an alternative
%  and other feature selection techniques. 
We have been working on a data set that includes the complete sales
data for books published in Spain across several years. After an
initial exploratory phase using visualization techniques, we have
applied several feature selection techniques in order
to find out what are the variables that have more impact on sales, and
then used machine learning to create a model and forecast sales. 
The described methodology improves the forecasting running time  %with
                                %respect to what?- JJ
and is
eventually able to predict sales with remarkable accuracy. Moreover,
the proposed method was validated by the company that provided
the data and incorporated in a business intelligence tool for
publishers, % We shouldn't say this, it's outside the bounds of the
            % paper. Besides, it was a different technique - JJ
since the obtained models provide a reliable guidance on the decision process of
publishing a book, without human intervention 
either for the operation or for interpretation.
% Antonio - esto es cierto??? :D
% We should simply say: 
% The method presented here provides a reliable data processing
% technique for editorial data and also yields a reasonable result
% that allows publishers to forecast sales and then create the
% appropriate print run without incurring in losses. 
%
% Besides, if this is true:
% It also provides a method that is able to provide insight on the
% decisions that have an influence on the print run for publishers. 
\end{abstract}

@@

The rest of this paper is structured as follows: next, 
Section \ref{sec:soa} presents a comprehensive review of the
approaches found in the bibliography related to the prediction of
sales from product characteristics. 
Then, Section \ref{sec:problem} describes the 
problem of how many books should be printed when a new book is published, 
        % no es el problema de publicación, es el problema de venta
        % de libros sin publicar. Habrá que buscar un nombre - JJ
        %[Pedro] cierto, lo cambio, aunque me ha quedado un nombre muy largo  :)
 followed by Section \ref{sec:methodology} where the
experimental setup and the methodology considered in the study is
presented.  %FERGU: mejor described para no repetir
Section \ref{sec:experiments} reports and analyzes the obtained results with a 
real dataset. Finally, conclusions and future work are presented in Section
\ref{sec:conclusionsAndFutureWork}. 
% Antonio - TODO: rescribir con los contenidos finales del artículo. ;)

@@

For this reason, usually the methods used to predict book sales have
been generally based on experts' experience.% Reference - JJ
 They analyse data about
sales and, taking into account their knowledge in industry, their
experience, and their perception about trends, could make decisions on
the companies production (how many books should be printed when a new
book is published). 
%FERGU: quitad los paréntesis :)
% Fergu: quítalos tú, tío, aquí puede editar todo el mundo - JJ
This is a complex problem, since the predictions are influenced by
external variables that must be taken into account, such as
seasonality, promotions or fashions that expert managers might
subjectively apply \cite{Lapide1999,ChingChin2010,ChernWSF15}. % This
                                % has something to do with the
                                % previous paragraph? Put it there!!! 
%
  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
  %  o aconsejar acerca de la cantidad de libros a imprimir.
  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
  %  sobre "Use Blog Information As Book Sales Prediction":
  %     Moon2010ICSSSM
  %     Moon2010ICEC
Recently, some works have proposed analyzing relationships between on-line information 
and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}. Specifically, Moon
et al. propose using the number of blog references as an indicator of
the success of a book, and thus, its sales. Different sales patterns
are observed by analysing data obtained. 
% Antonio - describir esos 'sales patterns'. ;)
% FERGU: y también cuales son esos 'data obtained'
However, the authors used in these papers historical data from published books, 
so their proposed methodology can not be applied to the problem of unpublished-books sales prediction.
%FERGU: pero nosotros también usamos historical data, no? qué diferencia hay con lo nuestro? por qué lo nuestro es lo mejor?

@@

  %[Pedro] otro caso muy similar es el paper de ChingChin2010 sobre:
  % New tea product
  % New cosmetic product
  % New soft drink product
In \cite{ChingChin2010}, a decision-support system for new product sales %FERGU: The work of Chinchin et al.?
forecasting is proposed to solve three real-world sales forecasting problems, namely: new tea, cosmetics, and soft drink products. This is addressed taking into account quantitative variables.
% Antonio - qué significa eso?
In that study, products are classified based on their sales patterns, so it is assumed that products in the same class would follow a similar sales pattern. 
However, as the authors state, the proposed system can not deal with qualitative 
data related to the products. Moreover, real-world cases, such as consumer 
electronics and fashion products, should be deeply analyzed, as these industries 
present/launch new products every season.

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
  % sales forecasting in printed circuit board industry.
In those cases where historical data are available, classical time series 
forecasting methods can be applied, which is what the authors do in
\cite{Chang2009}, where a hybrid model integrating K-Means and fuzzy
neural networks to forecast the future sales of a printed circuit
board is proposed. % We have been talking above that above and SAID IT
                   % DIDN'T WORK? Why do we say it here again? - JJ
A similar method is described by Chern et al. \cite{ChernWSF15}, who analyse 
historical data along online reviews, reviewer characteristics and review 
influences to understand how electronic `word-of-mouth' influences product sales. The proposed method is suitable for those sales forecasting problems with a big amount of online reviews and historical data.

@@

%-------------------------------------------------
\subsection{Data preprocessing and initial analysis}

@@

Specifically, the following forecasting methods are proposed: % Proposed why? - JJ
\begin{itemize}

@@

%An intro should go here - JJ

@@

All experiments are performed using 10-fold cross validation. The
dataset is partitioned into 10 parts where the training process is
carried out on 9 parts then the resulted model is tested on the left
10th part. This process is repeated 10 times, each time the model is
trained using different 9 parts. At the end of the process the 10
evaluation results on the testing parts are averaged.

@@

Once the methods to be applied have been chosen, they must be applied to the datasets to obtain the prediction models for each one. 
Later on, the models ability must be validated on non-previously seen data.
Specifically, instead of using the conventional validation strategy based on 
using a training set and later on a testing set (unknown data against which 
the model must be tested), a cross-validation technique \cite{Geisser1993,Kohavi1995,Devijver1982} 
has been used to estimate how accurately the predictive model will perform in 
practise. %, limiting at the same time the overfitting problem.

%
% TODO: explicar los resultados obtenidos en la selección de variables: 
%  (1) con el SOM, (2) con los métodos de selecc. vars.
%
% CONTAR COMO SE HAN PLANIFICADO LAS EJECUCIONES CON LOS DIFERENTES METODOS:
% - se ha usado la implementación de estos 5 métodos del paquete WEKA
% - se han realizado 30 ejecuciones con cada método
% - se ha usado una máquina Linux, Intel(R) Core(TM) i5-4430 CPU at 3.00GHz (4 cores) and 16 GB RAM
To do so, in a first stage, the feature selection process has been carried out 
using both the {\tt CfsSubsetEval} \cite{Hall1998} (a correlation-based feature subset 
evaluation method) and the ReliefFAttributeEval \cite{RobnikSikonja1997} (an 
adaptation of relief for attribute estimation) evaluation methods, implemented 
in the Weka tool.

% con ReliefFAttributeEval salen seleccionadas (9):
% print_run num_reprints tot_points_sale tot_points_sale_1st_year reprints distrib_novelty weeks_sale + total_sales
Using the {\tt ReliefFAttributeEval} feature selection method, and taking into account 
the best ranked attributes, the following variables have been selected: 
\emph{print-run, number of reprints, total points of sale, total points of sale 
1st year, reprints, units distributed as novelty, weeks for sale, total sales}.

% con CfsSubsetEval salen seleccionadas (4):
% num_reprints tot_points_sale print_run + total_sales
Using the {\tt CfsSubsetEval} feature selection method, the following variables have 
been selected: \emph{number of reprints, total points of sale, print-run, total sales}.
%FERGU: podeis quitar estos parrafos de variables porque ya está la tabla :)

%*************************************** SOM ANALISYS
% como tercer método, se ha usado el SOM; tras interpretar los mapas, se
% seleccionaron las variables más adecuadas.
Then, an analysis of the SOM results has been carried out in order to 
determine the best variables to be considered to build the forecasting model.

Further important preprocessing steps are carried out before applying the SOM analysis.
First, in order to label the U-matrix with total-sales values, this
variable is converted from numerical to categorical. Five categories
have been created to represent the quantities of sales of each book:
Very Low (VL), Low (L), Medium (M), High (H) and Very High (VH). Table
\ref{table:freq} shows the ranges of total-sales that correspond to
each category along with the number of books that fall in. Table
\ref{table:freq} and Figure \ref{fig:count} reveal more information
about the nature of the dataset. We can notice that most of 77\% of
the book are categorised as VL and L with limited number of sales. On
the other side, the books that achieved more than 2000 sold copies are
just around 4\%. This makes the problem of identifying those two
categories much harder. The new categorical feature is used to replace
the old numerical Total Sales feature in the SOM analysis.

\begin{table*}[ht]
\caption{Categories corresponding to total-sales variable. }
\centering{}%
\begin{tabular}{|c|c|c|c|}
\hline 
Category & Range of total sales & Count & Ratio\tabularnewline
\hline 
\hline 
Very Low & 1-100 & 2233 & 36.71\%\tabularnewline
\hline 
Low & 100-500 & 2323 & 38.19\%\tabularnewline
\hline 
Medium & 500-2000 & 1239 & 20.37\%\tabularnewline
\hline 
High & 2000-5000 & 224 & 3.68\%\tabularnewline
\hline 
Very High & $>$5000 & 64 & 1.05\%\tabularnewline
\hline 
\end{tabular}
\label{table:freq}
\end{table*}

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.60]{freq_sales.eps}
\end{center}
\caption{Number of books in each category.}
%This should go also to exploratory data analysis, that is, problem
%description - JJ
\label{fig:count}
\end{figure*}

Second, two categorical features (i.e; Editorial and Collection) are
removed from the analysis since they have large number of unique
different values and therefore they are less informative. Moreover,
four features (i.e; Subject1, Subject2, Subject3 and Book-binding)
have more than 10\% missing values so they are removed also.

Finally, the resulted dataset consisted of ten features including the
new Total Sales categorical feature. The SOM algorithm is trained
based on the nine numerical variables while the new total-sales
variable is used to label this data. The SOM algorithm is applied with
a large map size of $26 \times 16$  in order to represent the
data. The best SOM training results are obtained with a final
quantisation error of 0.691 and topographic error of 0.046.

In Figure \ref{fig:Umatrix} we label the U-matrix with the total-sales
categories. It can be clearly seen that the SOM algorithm has
successfully clustered the labels of the Total Sales into clear
identified regions. %So what? - JJ
 In the top of the U-matrix the VL category is
located. The L category appears in the middle of the matrix. Most of
the M category appears in bottom-right corner while the H and VH
categories are concentrated in the bottom-left corner.
% OK, this means that these features are more or less clearly
% separable. But the problem is that the UMatrix shows only 2, maybe 3
% clusters: vh and H. That's it. If you know UMatrix, that's what you
% see - JJ
By inspecting \texttt{num\_reprints}, \texttt{gifts},
\texttt{distrib\_novelty}, \texttt{tot\_points\_sale},
\texttt{tot\_points\_sale\_1st\_year} and \texttt{print\_run}
components, it can be noticed that they have the highest similarity to
the clusters shown in the U-matrix. Based on this analysis, those
features will be selected for the next stage.
%  This is not a result, it is data preprocessing. You should have
%  included it in the 4th section. All results do not need to go into
%  the "REsults" section, only the final results. 
% Besides, are you using this or feature selection for selecting
% features?

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.4]{SOM_figure.eps}
\end{center}
\caption{U-matrix and component planes.}
\label{fig:componentplanes}
\end{figure*}

\begin{figure*}[http] 
\begin{center} 
\begin{tabular}{cc}
\includegraphics[scale=0.55]{Umatrix.eps}  &
\includegraphics[scale=0.55]{Labels.eps}  \\
U-matrix & Labels 
\end{tabular}
\end{center} 
\caption{Labeling the U-matrix using the total-sales variable.}
\label{fig:Umatrix} 
\end{figure*}

%*************************************** SOM ANALISYS

\begin{table}
\begin{tabular}[htb]{|c|c|c|c|c|}
\hline
Variable  & Pre-Sales & ReliefFAttributeEval  & SOM & CfsSubsetEval \\ \hline \hline
subject1    & $\checkmark$  &   &   &   \\ \hline
subject2    & $\checkmark$  &   &   &   \\ \hline
subject3    & $\checkmark$  &   &   &   \\ \hline
editorial   & $\checkmark$  &   &   &   \\ \hline
collection  & $\checkmark$  &   &   &   \\ \hline
binding   & $\checkmark$  &   &   &   \\ \hline
ret\_price    & $\checkmark$  &   &   &   \\ \hline
reprints    & $\checkmark$  & $\checkmark$  &   &   \\ \hline
num\_reprints    & $\checkmark$  & $\checkmark$  & $\checkmark$  & $\checkmark$  \\ \hline
gifts   & $\checkmark$  &   & $\checkmark$  &   \\ \hline
distrib\_novelty   & $\checkmark$  & $\checkmark$  & $\checkmark$  &   \\ \hline
tot\_points\_sale   & $\checkmark$  & $\checkmark$  & $\checkmark$   & $\checkmark$  \\ \hline
tot\_points\_sale\_1st\_year    & $\checkmark$  & $\checkmark$  &  $\checkmark$ &   \\ \hline
weeks\_sale    & $\checkmark$  & $\checkmark$  &   &   \\ \hline
print\_run   & $\checkmark$  & $\checkmark$  & $\checkmark$  & $\checkmark$  \\ \hline
total\_sales   & $\checkmark$  & $\checkmark$  & $\checkmark$  & $\checkmark$  \\ \hline

\end{tabular}
\caption{Variables used in each method.} %PABLO: Poned este caption bien
\label{tab:varmethods}
\end{table}

Table \ref{tab:varmethods} shows the used variables used in each step. %Pablo: poner también esta frase mejor 
Once the different reduced datasets have been obtained, proposed methods 
(M5P, LR, SVM, kNN, MLP) have been selected for this study from 
the Weka implementation, and they were run 30 times with the Weka default parameter 
settings and a different random initialisation seed for each run and each dataset.

Experiments have been conducted on an Intel(R) Core(TM) i5-4430 CPU at 3.00GHz 
(4 cores) and 16 GB RAM, running Ubuntu Linux 14.04.1 LTS and Java JRE\_1.7.0\_72.

>>>>

%%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%
\author {
P.A. Castillo$^1$, A.M. Mora$^1$, H. Faris$^2$, J.J. Merelo$^1$, \\ P. Garc\'{\i}a-S\'anchez$^1$, A.J. Fern\'andez-Ares$^1$, M.G. Arenas$^1$, P. de las Cuevas$^1$
}
\institute{
$^1$Department of Computer Architecture and Computer Technology. CITIC, ETSIIT. University of Granada (Spain)\\
$^2$Business Information Technology Department. King Abdullah II School for Information Technology. The University of Jordan. Amman (Jordan)\\
           e-mail: {\tt pacv@ugr.es}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
When a new book is launched the publisher faces the problem of
how many books should be printed for delivery to bookstores. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. In this
paper, we are tackling the problem of predicting total sales in order to 
print the right amount of books, doing so even before the book has
reached the shelves. 
Several years 
% % Antonio - Decir cuántos años son, que no me acuerdo.
% of data on published books in Spain have been processed by means of
% data visualisation %visualization does not "process". I propose an alternative
%  and other feature selection techniques. 
We have been working on a data set that includes the complete sales
data for books published in Spain across several years. After an
initial exploratory phase using visualisation techniques, we have
applied several feature selection techniques in order
to find out what are the variables that have more impact on sales, and
then used machine learning to create a model and forecast sales. 
The described methodology improves the forecasting running time  %with
                                %respect to what?- JJ
and is
eventually able to predict sales with remarkable accuracy. Moreover,
the proposed method was validated by the company that provided
the data and incorporated in a business intelligence tool for
publishers, % We shouldn't say this, it's outside the bounds of the
            % paper. Besides, it was a different technique - JJ
since the obtained models provide a reliable guidance on the decision process of
publishing a book, without human intervention 
either for the operation or for interpretation.
% Antonio - esto es cierto??? :D
% We should simply say: 
% The method presented here provides a reliable data processing
% technique for editorial data and also yields a reasonable result
% that allows publishers to forecast sales and then create the
% appropriate print run without incurring in losses. 
%
% Besides, if this is true:
% It also provides a method that is able to provide insight on the
% decisions that have an influence on the print run for publishers. 
\end{abstract}

@@

The rest of this paper is structured as follows: next, 
Section \ref{sec:soa} presents a comprehensive review of the
approaches found in the bibliography related to the prediction of
sales from product characteristics. 
Then, Section \ref{sec:problem} describes the 
problem of how many books should be printed when a new book is published, 
        % no es el problema de publicación, es el problema de venta
        % de libros sin publicar. Habrá que buscar un nombre - JJ
        %[Pedro] cierto, lo cambio, aunque me ha quedado un nombre muy largo  :)
 followed by Section \ref{sec:methodology} where the
experimental setup and the methodology considered in the study is
presented.  %FERGU: mejor described para no repetir
Section \ref{sec:experiments} reports and analyses the obtained results with a 
real dataset. Finally, conclusions and future work are presented in Section
\ref{sec:conclusionsAndFutureWork}. 
% Antonio - TODO: rescribir con los contenidos finales del artículo. ;)

@@

For this reason, usually the methods used to predict book sales have
been generally based on experts' experience.% Reference - JJ
 They analyse data about
sales and, taking into account their knowledge in industry, their
experience, and their perception about trends, could make decisions on
the companies production (how many books should be printed when a new
book is published). 
%FERGU: quitad los paréntesis :)
% Fergu: quítalos tú, tío, aquí puede editar todo el mundo - JJ
This is a complex problem, since the predictions are influenced by
external variables that must be taken into account, such as
seasonality, promotions or fashions that expert managers might
subjectively apply \cite{Lapide1999,ChingChin2010,ChernWSF15}. % This
                                % has something to do with the
                                % previous paragraph? Put it there!!! 
%
  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
  %  o aconsejar acerca de la cantidad de libros a imprimir.
  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
  %  sobre "Use Blog Information As Book Sales Prediction":
  %     Moon2010ICSSSM
  %     Moon2010ICEC
Recently, some works have proposed analysing relationships between on-line information 
and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}. Specifically, Moon
et al. propose using the number of blog references as an indicator of
the success of a book, and thus, its sales. Different sales patterns
are observed by analysing data obtained. 
% Antonio - describir esos 'sales patterns'. ;)
% FERGU: y también cuales son esos 'data obtained'
However, the authors used in these papers historical data from published books, 
so their proposed methodology can not be applied to the problem of unpublished-books sales prediction.
%FERGU: pero nosotros también usamos historical data, no? qué diferencia hay con lo nuestro? por qué lo nuestro es lo mejor?

@@

  %[Pedro] otro caso muy similar es el paper de ChingChin2010 sobre:
  % New tea product
  % New cosmetic product
  % New soft drink product
In \cite{ChingChin2010}, a decision-support system for new product sales %FERGU: The work of Chinchin et al.?
forecasting is proposed to solve three real-world sales forecasting problems, namely: new tea, cosmetics, and soft drink products. This is addressed taking into account quantitative variables.
% Antonio - qué significa eso?
In that study, products are classified based on their sales patterns, so it is assumed that products in the same class would follow a similar sales pattern. 
However, as the authors state, the proposed system can not deal with qualitative 
data related to the products. Moreover, real-world cases, such as consumer 
electronics and fashion products, should be deeply analysed, as these industries 
present/launch new products every season.

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
  % sales forecasting in printed circuit board industry.
In those cases where historical data are available, classical time series 
forecasting methods can be applied, which is what the authors do in
\cite{Chang2009}, where a hybrid model integrating K-Means and fuzzy
neural networks to forecast the future sales of a printed circuit
board is proposed. % We have been talking above that above and SAID IT
                   % DIDN'T WORK? Why do we say it here again? - JJ
                   % No, above we said that the efficiency depends on the field 
                   % of application and the available problem data. - pedro
A similar method is described by Chern et al. \cite{ChernWSF15}, who analyse 
historical data along online reviews, reviewer characteristics and review 
influences to understand how electronic `word-of-mouth' influences product sales. 
The proposed method is suitable for those sales forecasting problems 
with a big amount of online reviews and historical data.

@@

%-------------------------------------------------
\subsection{Data preprocessing and initial analysis}
\label{subsec:data_preproces}

@@

Specifically, the following forecasting methods are proposed: 
        % Proposed why? - JJ
        % because those methods were those that could lead with the problem data - pedro
\begin{itemize}

@@

% An intro should go here - JJ
% Antonio - done

This section presents the experiments conducted over the dataset considering the pre-sales variables forecasting new book sales.
Feature selection techniques have been also applied in order to test their utility by comparing the obtained results.

We have analysed the whole dataset (all the editorials), but also performed some experiments considering specific editorials as example cases.
The obtained decision trees have been plotted to show their simplicity and their real value as a decision-aid tool for editors.

%--------------------------------------------------------------------------

@@

All experiments are performed using 10-fold cross validation \cite{Geisser1993,Kohavi1995,Devijver1982}. The dataset is partitioned into 10 parts where the training process is carried out on 9 parts then the resulted model is tested on the left 10th part. This process is repeated 10 times, each time the model is trained using different 9 parts. At the end of the process the 10 evaluation results on the testing parts are averaged. 
This technique is used to estimate how accurately the predictive model will perform in practise, limiting, at the same time, the overfitting problem.

In addition, due to the stochastic component present in some of the methods and also in order to evaluate the running time, 30 repetitions of each experiment have been done per method. Then the average and standard deviation have been computed.

***TODO***: talking about the machines used

%Experiments have been conducted on an Intel(R) Core(TM) i5-4430 CPU at 3.00GHz 
%(4 cores) and 16 GB RAM, running Ubuntu Linux 14.04.1 LTS and Java JRE\_1.7.0\_72.

%--------------------------------------------------------------------------

\subsection{Results for all the editors}
\label{subsec:results_all_editors}

In the first experiment, forecasting methods have been applied to the whole dataset. All the pre-sales features have been considered. Obtained results are presented in Table \ref{tab:all_editors_no_fs}.

\begin{table}
\caption{Predicting Total sales for all editors (all the features). 30 repetitions, 10-fold cross validation.
\label{tab:all_editors_no_fs}}
\centering{}%
\begin{tabular}{|c|l|l|l|l|l|l|}
\hline 
 & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
K-NN & 0.787 $\pm$ 0.08 & 272.294 $\pm$ 32.38 & 840.594 $\pm$ 240.11 & 47.475 $\pm$ 3.39 & 63.072 $\pm$ 10.29 & 0.001 $\pm$ 0.01\tabularnewline
\hline
M5P & 0.890 $\pm$ 0.09 & 214.365 $\pm$ 22.96 & 634.229 $\pm$ 307.76 & 37.457 $\pm$ 3.12 & 48.324 $\pm$ 25.16 & 18.845 $\pm$ 0.61\tabularnewline
\hline 
Random Forest & 0.840 $\pm$ 0.05 & 253.365 $\pm$ 29.43 & 788.937 $\pm$ 282.01 & 44.164 $\pm$ 2.76 & 57.766 $\pm$ 8.15 & 4.906 $\pm$ 0.12\tabularnewline
\hline 
Linear Regression & 0.872 $\pm$ 0.07 & 308.679 $\pm$ 25.44 & 680.905 $\pm$ 226.41 & 54.053 $\pm$ 4.38 & 52.130 $\pm$ 18.29 & 984.687 $\pm$ 128.21\tabularnewline
\hline 
SVM & 0.876 $\pm$ 0.04 & 248.763 $\pm$ 27.49 & 732.641 $\pm$ 260.56 & 43.371 $\pm$ 2.35 & 53.471 $\pm$ 6.29 & 6169.239 $\pm$ 281.49\tabularnewline
\hline 
\end{tabular}
\end{table}

***TODO***: the results show...

%--------------------------------------------------------------------------

\subsection{Feature selection}
\label{subsec:feature_selection}

In this second experiment, different feature selection processes have been applied.

***TODO***: The aim of these techniques is to reduce the number of features to consider...
% Antonio - TODO: explain the aim of FS in these experiments.

We have used both the {\tt CfsSubsetEval} \cite{Hall1998} (a correlation-based feature subset evaluation method) and the ReliefFAttributeEval \cite{RobnikSikonja1997} (an adaptation of relief for attribute estimation) evaluation methods, implemented in the Weka tool and described in Section \ref{subsec:data_preproces}.

Then, the dataset has been projected using SOM, and a visual analysis of the obtained results has been carried out in order to determine the best variables to consider.
An important preprocessing step has been carried out before conducting the SOM analysis, so the two categorical features Editorial and Collection have been
removed from the analysis since SOM cannot deal with them without a previous transformation into numerical ones. However, since they have a large number of unique different values this would be finally impracticable and useless.

Moreover,
four features (i.e; Subject1, Subject2, Subject3 and Book-binding)
have more than 10\% missing values so they are removed also.

***TODO***: describe the parameters of SOM (size, neighbourhood shape, etc) and obtained quantisation and topographical errors.

% The SOM algorithm is applied with a large map size of $26 \times 16$  in order to represent the data. The best SOM training results are obtained with a final quantisation error of 0.691 and topographic error of 0.046.

***TODO***: Justify the selected features by SOM (why have we chosen them?).

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.4]{som_planes.eps}
\end{center}
\caption{U-matrix and component planes.}
\label{fig:componentplanes}
\end{figure*}

%\begin{figure*}[http] 
%\begin{center} 
%\begin{tabular}{cc}
%\includegraphics[scale=0.55]{Umatrix.eps}  &
%\includegraphics[scale=0.55]{Labels.eps}  \\
%U-matrix & Labels 
%\end{tabular}
%\end{center} 
%\caption{Labeling the U-matrix using the total-sales variable.}
%\label{fig:Umatrix} 
%\end{figure*}

The selected features per method are shown in Table \ref{tab:features_selected}.

\begin{table}
\caption{Features selected by each method 
\label{tab:features_selected}}
\centering{}%
\begin{tabular}{|c|c|c|c|c|}
\hline 
No. & Feature & ReliefFAttributeEva & CfsSubsetEval & SOM\tabularnewline
\hline 
1 & ret\_price & $\checkmark$ &  & $\checkmark$\tabularnewline
\hline 
2 & subject1 & $\checkmark$ & $\checkmark$ & $\checkmark$\tabularnewline
\hline 
3 &  Editorial+Collection &  &  & \tabularnewline
\hline 
4 & binding &  &  & \tabularnewline
\hline 
5 & gifts & $\checkmark$ &  & $\checkmark$\tabularnewline
\hline 
6 & distrib\_novelty & $\checkmark$ &  & \tabularnewline
\hline 
7 & tot\_points\_sale & $\checkmark$ &  & $\checkmark$\tabularnewline
\hline 
8 & tot\_points\_sale\_1st\_year & $\checkmark$ &  & \tabularnewline
\hline 
9 & weeks\_sale & $\checkmark$ &  & $\checkmark$\tabularnewline
\hline 
10 & print\_run & $\checkmark$ & $\checkmark$ & $\checkmark$\tabularnewline
\hline 
\end{tabular}
\end{table}

% Antonio - TODO: change the names (and font format) to the same as variables in previous tables

*************** TO CHANGE WITH THE NEW RESULTS **************

@@
